Concurrent Programming with CXL

### 2020-06-07 book/paper.tex
Finished first draft of bounded buffer chapter.

@@

[RVR.  More here.]

>>>>

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{../PCsemadata.cxl}
\end{code}
\caption{Test whether the bounded buffer delivers the right data in the
right order.}
\label{fig:PCsemadata}
\end{figure}

@@

Figure~\ref{fig:PCsemadata} tests whether the correct data is sent in
the correct order.  There are the same number of producers and consumers.
Each producer $i$ produces two tuples: $(i, 0)$ and $(i, 1)$ in that order.
Each consumer consumes two tuples and checks that the tuples are different
and that, if the two tuples come from the same producer, then they have to
be in the order sent.
Moreover, consumers add the tuples they received to the set
\texttt{received} (atomically---a lock could have been used here as well).)
The \texttt{main()} process waits for all consumers to have received
exactly the set of tuples that the producers produce.
